Bayesian statistics and swine flu

### 2009-09-25 docs/pandemic/bayesPandemic.rnw
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@413 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\begin{frame}[fragile]
\frametitle{Hospital demand}
<<hospLoad,echo=T>>=
# generate hospital times
hospSample = simHospitals(paramSample , Ndays=60, 
	NinfectionsPerDay=c(seq(10, 100, len=30),seq(100, 10, len=30) ) )

>>>>

\begin{frame}[fragile]
\frametitle{Hospital demand}
<<hospLoad,echo=T>>=
# generate hospital times
hospSample = simHospitals(paramSample , Ndays=80, 
	NinfectionsPerDay=c(seq(1, 100, len=20),seq(100, 1, len=20), rep(2, 40) ) )
